---
title: "Publications, Research & Media"
toc: false
---

<!-- ## Journal Publications -->

```{r load-publications, echo=FALSE, message=FALSE, warning=FALSE}
library(RefManageR)
library(knitr)
library(dplyr)
library(kableExtra)

# Load the bibliography files
publications <- ReadBib("my_pubs.bib", check = FALSE)
working_papers <- ReadBib("my_working_papers.bib", check = FALSE)

# Function to format citations for display
format_citation <- function(bib) {
  # Format each entry
  formatted <- lapply(bib, function(entry) {
    authors <- entry$author
    if (length(authors) > 4) {
      authors <- paste0(authors[1], " et al.")
    } else {
      authors <- paste(authors, collapse = ", ")
    }
    
    title <- entry$title
    journal <- ifelse(!is.null(entry$journal), entry$journal, "Working Paper")
    year <- entry$year
    
    # Add volume and pages if available
    vol_pages <- ""
    if (!is.null(entry$volume)) {
      vol_pages <- paste0(", ", entry$volume)
      if (!is.null(entry$number)) {
        vol_pages <- paste0(vol_pages, "(", entry$number, ")")
      }
      if (!is.null(entry$pages)) {
        vol_pages <- paste0(vol_pages, ", pp. ", entry$pages)
      }
    }
    
    # Format the full citation
    citation <- paste0("<p><strong>", authors, " (", year, ")</strong>. ", 
                      title, ". <em>", journal, "</em>", vol_pages, ".</p>")
    
    return(citation)
  })
  
  return(paste(formatted, collapse = "\n"))
}
```

## Published Articles

::: {.research-papers}


```{r published-papers, echo=FALSE, results='asis'}
cat(format_citation(publications))
```

:::



## Working Papers

::: {.research-papers}

```{r working-papers, echo=FALSE, results='asis'}
cat(format_citation(working_papers))
```

:::


## Media Coverage

::: {.media-coverage}

<div class="media-item">
<div class="media-date">December 2024</div>
<div class="media-title"><a href="https://esb.nu/economenparade-2024/">Media Coverage for Economenparade 2024 (in Dutch)</a></div>
<div class="media-source"><em>ESB</em></div>
</div>

<div class="media-item">
<div class="media-date">July 2023</div>
<div class="media-title"><a href="https://clsbluesky.law.columbia.edu/2023/07/12/can-integrity-pledges-improve-financial-reporting/">Can Integrity Pledges Improve Financial Reporting?</a></div>
<div class="media-source"><em>Columbia Law School Blue Sky Blog</em></div>
</div>

<div class="media-item">
<div class="media-date">April 2023</div>
<div class="media-title"><a href="https://www.l-iz.de/bildung/medien/2023/04/prognose-nachrichtenwusten-bis-2025-sind-rund-40-prozent-ohne-lokalzeitung-524584">Prognose: Nachrichtenwüsten – bis 2025 sind rund 40 Prozent der deutschen Gemeinden ohne Lokalzeitung</a></div>
<div class="media-source"><em>Leipziger Internet Zeitung</em></div>
</div>

<div class="media-item">
<div class="media-date">April 2023</div>
<div class="media-title"><a href="https://www.kleinezeitung.at/kultur/medien/6120796/Ergebnisse-von-USForschern_Studie_Ohne-lokale-Medien-steigt-die">Studie: Ohne lokale Medien steigt die Kriminalität</a></div>
<div class="media-source"><em>Kleine Zeitung</em></div>
</div>

<div class="media-item">
<div class="media-date">April 2022</div>
<div class="media-title"><a href="https://www.zeit.de/2022/16/lokaljournalismus-rueckgang-zeitung-schliessung">Sie geben nicht auf</a></div>
<div class="media-source"><em>ZeitOnline</em></div>
</div>

<div class="media-item">
<div class="media-date">August 2022</div>
<div class="media-title"><a href="https://www.latimes.com/business/story/2022-08-29/decline-of-local-news?consumer=googlenews">Column: How the decline of local news exposes the public to lies and corruption</a></div>
<div class="media-source"><em>Los Angeles Times</em></div>
</div>

<div class="media-item">
<div class="media-date">January 2022</div>
<div class="media-title"><a href="https://www.manager-magazin.de/harvard/management/kriminalitaet-von-managern-die-fehlende-kontrolle-der-presse-a-f22d69e5-0002-0001-0000-000185432237">Die Zeitung geht unter, das Verbrechen kommt</a></div>
<div class="media-source"><em>Manager Magazin</em></div>
</div>

<div class="media-item">
<div class="media-date">Winter 2021</div>
<div class="media-title"><a href="https://niemanreports.org/articles/a-green-light-for-corruption/">A Green Light for Corruption</a></div>
<div class="media-source"><em>Nieman Reports</em></div>
</div>

<div class="media-item">
<div class="media-date">October 2021</div>
<div class="media-title"><a href="https://www.sandiegouniontribune.com/columnists/story/2021-10-22/column-study-says-corporate-misbehavior-increases-after-local-newspapers-shut-down">Column: Corporate misbehavior increases after local newspapers shut down, study says</a></div>
<div class="media-source"><em>San Diego Union Tribune</em></div>
</div>

<div class="media-item">
<div class="media-date">October 2021</div>
<div class="media-title"><a href="https://www.sueddeutsche.de/wirtschaft/lokalzeitungen-umweltkriminalitaet-studie-1.5444839">Warum Lokalzeitungen für gutes Klima sorgen</a></div>
<div class="media-source"><em>Süddeutsche Zeitung</em></div>
</div>

<div class="media-item">
<div class="media-date">October 2021</div>
<div class="media-title"><a href="https://hbswk.hbs.edu/item/how-newspaper-closures-open-the-door-to-corporate-crime">How Newspaper Closures Open the Door to Corporate Crime</a></div>
<div class="media-source"><em>Harvard Business School Working Knowledge</em></div>
</div>

<div class="media-item">
<div class="media-date">August 2021</div>
<div class="media-title"><a href="https://corpgov.law.harvard.edu/2021/08/25/when-the-local-newspaper-leaves-town-the-effects-of-local-newspaper-closures-on-corporate-misconduct/">When the Local Newspaper Leaves Town: The Effects of Local Newspaper Closures on Corporate Misconduct</a></div>
<div class="media-source"><em>Harvard Law School Forum on Corporate Governance</em></div>
</div>

<div class="media-item">
<div class="media-date">February 2015</div>
<div class="media-title"><a href="https://clsbluesky.law.columbia.edu/2015/02/04/greater-disclosure-harms-cartels/">Greater Disclosure Harms Cartels</a></div>
<div class="media-source"><em>Columbia Law School Blue Sky Blog</em></div>
</div>
:::

